Kelompok 4_Praktikum_Pekan 8

### 2024-04-06 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
hist(normal_means, main = "Histogram Normal Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#8DC16D")
hist(uniform_means, main = "Histogram Uniform Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#4493CA")
hist(exponential_means, main = "Histogram Exponential Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#D44155")
```

>>>>

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
hist(norm_means, main = "Histogram Normal Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#8DC16D")
hist(unif_means, main = "Histogram Uniform Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#4493CA")
hist(exp_means, main = "Histogram Exponential Mean", 
     xlab = "Mean", ylab = "Frequency", col = "#D44155")
```
